
\chapter{State of the art} 
\label{ch:Chapter2}
\vfill \minitoc \newpage

It's possible to identify some applications that include an event planning function: \textit{\cite{facebook}}, \textit{Doodle}, \textit{\cite{superplanner}}, and \textit{\cite{asana}}. The first two listed, \textit{Facebook} and \textit{Doodle}, both support the creation of events, but they focus on scheduling while also allowing for some basic functionalities like invitation of people to the event. 

\textit{Super Planner} allows for more complex event management, providing calculators for venue capacity, food/catering and staffing, as well as others for managing a budget limit. 

\textit{Asana} can be used to assign tasks to people and manage the work that needs to be done. However, none of these have a focus on collaboration between people focused on an event. While \textit{Asana} has the capability of assigning tasks between people, it serves more as a work management tool to organize teams in business projects.

\textit{Super Planner} has good tools to manage an event, but lacks collaboration between people and invitation of people to the event is not possible. 

\textit{Facebook} and Doodle are great tools for basic event planning, but do not offer much more than setting a location, date and giving a description of the event. It is important to mention that \textit{Facebook} does offer some tools that could prove useful, such as posting a message in the event page, but that are not specifically made for this purpose and end up being too cumbersome.

The current state of the art now counts with a really similar application to what we are proposing, an application called \textit{\cite{eventbrite}}.
This application has a really similar concept but in a different way. First of all it implements a ticket system. Defining an event requires you to make a ticket price, which is not ideal since the group wants the event's expenses to be modifiable throughout the event, implementing a voting system for it if wanted. There are others that are more focused on team management, for projects, like \textit{\cite{cvent}} and \textit{\cite{xingevents}} and then there are ones like \textit{EventBrite} that implement a ticket system like \textit{Ticket Taylor}. 

%Also one has to create an account to use this platform, which is not ideal because it's limiting of a big user base as people are normally reluctant to create accounts on platforms as there are too many is the current days.

Also one has to create an account to use this platform, which is not ideal because people are normally reluctant to create accounts on platforms as there are too many in the current days. 


As far as the group knows there are none that implement a division of tasks, expenses and playlist creation that have a focus on collaboration of people, as well as multimedia functionality. These features make sense together in an event planning app as a big volume of events contain all of these aspects in common.