
\prefacesection{Abstract}


\noindent

The digital postcard application developed in this project aims to bring back the charm of sending postcards in the digital age. With the rise of instant messaging and social media, the traditional practice of sending postcards has diminished. However, we believe that there is still value in the personal touch and sentimentality that postcards offer, and our application seeks to bridge the gap between generations and provide a modernized yet traditional means of communication.

By leveraging technology, we have created a platform where users can create, personalize, and send digital postcards to their loved ones. The application captures the essence of traditional postcards by providing customizable templates, allowing users to add their own messages and images. Users can unleash their creativity and design unique postcards that reflect their personality and emotions.

The application is built on a client-server architecture, with the Android application serving as the client and a web \gls{api} as the server. This architecture allows for seamless communication between the user's device and the server, enabling quick and reliable delivery of postcards. The use of modern technologies, such as Android Compose, ensures a smooth and visually appealing user interface, enhancing the overall experience.

Through this project, we aim to address the generation gap by providing a platform that appeals to both younger and older generations. The digital nature of the postcards caters to the tech-savvy younger generation, while the traditional sentimentality of the practice resonates with older generations who appreciate the nostalgic value of postcards.

In conclusion, this project showcases the power of technology to revive and adapt traditional practices for the modern era. By combining the convenience of digital communication with the emotional connection of handwritten postcards, our application offers a unique and meaningful way to stay connected with loved ones. As we continue to refine and expand this project, we hope to inspire more people to embrace the beauty of postcards and foster meaningful connections in an increasingly digital world.

\vspace*{1em}

\textbf{\large{Keywords:}} Written Postcards, Digital Postcards, Generation Gap, Client-Server Application, Android Compose.


%\begin{itemize}
%	
%	
%	\item Events - Something that takes place (in this case social events);
%	\item Item - Associated with events, these are the objects of an event;
%	\item Task - An action that needs to be done by a participant in an Event;
%	\item User - Person that uses the platform, normally comprised of a Name, Email and Phone Number;
%	\item Invite - Asking for someone to go to an Event.
%	
%\end{itemize}

%
%
%\cleardoublepage
%
%
%\prefacesection{Acronyms}
%
%
%
%\vspace{3em}
%
%\noindent
%
%%\textbf{\large{Acronyms:}} 
%
%\acrshort{orm} stands for \acrfull{orm}.
%
%\acrshort{crud} stands for \acrfull{crud}.
%
%\acrshort{ide} stands for \acrfull{ide}.





